---
title: "Bob Ross Palette"
author: "Nujcharee Haswell"
date: "17/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<iframe width="560" height="315" src="https://www.youtube.com/embed/lLWEXRAnQd0" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Just another night Netflix binge watching while doing some dataviz projects.

I am no artist but I do appreciate good piece of art work. Recently, discovered a programme on Netflix called **Chilling with Bob Ross** and quickly he becomes one of my idols.

Check out his palette and choices of colours. 
What is Grimson Blue? What about Titanium White? 
Little that I know, there are so many shades of blue!

Spending most of my day working with HEX codes, I wonder if I can find "Grimson Blue" - Hex code style...??

```{r message=FALSE}
library(paletter)
library(png)
download.file("https://www.twoinchbrush.com/images/painting373.png", "image.png")
painting     <- readPNG("image.png")
```

### Bob Ross' ISLAND IN THE WILDERNESS
```{r message=FALSE}
grid::grid.raster(painting)


dimension    <- dim(painting)
painting_rgb <- data.frame(
  x = rep(1:dimension[2], each = dimension[1]),
  y = rep(dimension[1]:1, dimension[2]),
  R = as.vector(painting[,,1]), #slicing our array into three
  G = as.vector(painting[,,2]),
  B = as.vector(painting[,,3])
)

k_means        <- kmeans(painting_rgb[,c("R","G","B")], centers = 20, iter.max = 30)
```
## What is grimson blue in hex code?

```{r}
show_col(rgb(k_means$centers))
```

As the man himself said "The most fun part of this, is washing the brush...."

As for me, the fun part is finding grimson blue in Hex code. 



